Assessment of the KLGO Coastal Waterbird Survey Monitoring Program

### 2018-11-09 analysis/paper/paper.Rmd
Ran into some errors with the CSV general retrial script; will look into it
Finally fixed the error that was blocking the retrieval script. Script now collects all .csv files as data frames for future use.
moved library loads from scripts to 'setup' code chunk at front of Rmd

library(dply);library(ggplot2);library(dbplyr);

```

@@

###########
# MADELEINE WILL REPLACE WITH CODE TO VARIOUS TABLES FROM CSV FILES
###########
```

>>>>

library(dplyr);library(ggplot2);library(dbplyr);library(readr)

```
# Things To Discuss
- add all libraries used in scripts to 'setup' code chunk (just above) rather than just loading in script so that it is easy to see what needs to be loaded before you can successfully knit.

@@

source("./analysis/scripts/data_retrievalCSVs.R")
```
